---
title: "Data Products - Course Project - Linear Regression for MTCARS"
author: "XVALDA"
date: "30 July 2017"
output: ioslides_presentation
---

## Overview

This shiny application is developed within the scope of the final project of the Coursera "Developing Data Products" course. 

The project consists of two parts:   
- a shiny application deployed on R Studio servers  
- a pitch presentation  


The code is available on Github: https://github.com/xvalda/Coursera---Data-Products---Course-Project

The shiny application can be viewed here: https://xvalda.shinyapps.io/dataproductscourseproject/   


## Project summary

This is a very basic project, proposing to draw a linear regression between one regressor and one outcome.  
For each configuration we also display the intercept, the slope and the R-squared value of the linear model.  

The user can choose any variable as the outcome or the regressor.  

**Data**
We use the [mtcars](https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/mtcars.html) dataset in R.  

## Application - ui.R {.smaller}
<small>
```{r eval=FALSE, echo=TRUE}
library(shiny)
shinyUI(fluidPage(
    titlePanel(HTML("Linear relations between variables of the mtcars dataset")),
    # user inputs requested predictor and outcome
    sidebarLayout(
        sidebarPanel(
            h3("Choose a predictor (X-axis): "),
            selectInput("inputPredictor", label = NULL, choices = c("Displacement"="disp", "Cylinders"="cyl",
            "Miles per Gallon"="mpg", "Horsepower"="hp", "Rear Axle Ratio"="drat",
            "Weight"="wt", "1/4 Mile Time"="qsec", "vs"="vs",
            "Transmission"="am", "Gears"="gear", "Carburator"="carb")),
            h3("Choose the outcome variable (Y-axis): "),
            selectInput("inputOutcome", label = NULL, choices = c("Miles per Gallon"="mpg", "Cylinders"="cyl", "Displacement"="disp", "Horsepower"="hp", "Rear Axle Ratio"="drat", "Weight"="wt", "1/4 Mile Time"="qsec", "vs"="vs", "Transmission"="am", "Gears"="gear", "Carburator"="carb")),
            #show in side pane the intercept, slope and R-Squared
            h3("Intercept"),
            textOutput("interceptOut"),
            h3("Slope"),
            textOutput("slopeOut"),
            h3("R-Squared"),
            textOutput("rsquaredtOut")
            ),
        # Plot the liner model
        mainPanel(
            plotOutput("plotLM")
            )
        )
    ))
```
</small>

## Application - server.R {.smaller}

```{r eval=FALSE, echo=TRUE}
library(shiny)
data("mtcars")
shinyServer(function(input, output, session) {
    # PLOT
    fit <- reactive({
        lm(mtcars[,input$inputOutcome]~mtcars[,input$inputPredictor])
    })
    output$plotLM <- renderPlot({
        plot(mtcars[,input$inputPredictor], mtcars[,input$inputOutcome],
             xlab=input$inputPredictor, ylab=input$inputOutcome, cex = 1.5, pch = 16)
        abline(lm(mtcars[,input$inputOutcome]~mtcars[,input$inputPredictor]), col = "red", lwd = 2)
    })
    output$interceptOut <- renderText({
        summary(lm(mtcars[,input$inputOutcome]~mtcars[,input$inputPredictor]))$coef[1,1]
    })
    output$slopeOut <- renderText({
        summary(lm(mtcars[,input$inputOutcome]~mtcars[,input$inputPredictor]))$coef[2,1]
    })
    output$rsquaredtOut <- renderText({
        summary(lm(mtcars[,input$inputOutcome]~mtcars[,input$inputPredictor]))$r.squared
    })
})
```

